\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage[latin1] { inputenc}
\usepackage{changepage}
%\topmargin .5in
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}
%\rfoot{{\footnotesize Curriculum Vitae, Tomer D. Ullman, \thepage}}


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Tomer D. Ullman \vspace*{.1in}}

\begin{resume}

\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{2.75in}p{2in}}
Massachusetts Institute of Technology & (617)253-2010 \\
Department of Brain and Cognitive Sciences                        & \verb+tomeru@mit.edu+\\
77 Massachusetts Ave., Bldg. 46-4053            & \verb+http://www.mit.edu/~tomeru+\\
Cambridge, MA 02138 USA               & \\
\end{tabular}

\section{\sc Position}
Postdoctoral associate at the Center for Brains, Minds \& Machines (CBMM) working in Josh Tenenbaum's Computational Cognitive Science group at MIT, and Elizabeth Spelke's Infant Development lab at Harvard. 

\section{\sc Research Interests}
Computational cognitive modeling, Child development, probabilistic programming, machine learning, intuitive theories, folk physics, folk psychology, common sense, theory of the self

\section{\sc Education}

{\bf Massachusetts Institute of Technology}\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. in Brain and Cognitive Sciences (2008-2015)

\begin{list2}
\vspace*{.05in}
\item Dissertation Topic:  On the Nature and Origin of Intuitive Theories
\item Advisor: Josh Tenenbaum
\end{list2}
\end{list1}

{\bf Hebrew University of Jerusalem}\\
\vspace*{-.1in}
\begin{list1}
\item[] B.S.~in Physics and Cognitive Science, (double major, 2004-2008)

\begin{list2}
\vspace*{.05in}
\item \textit{Magna Cum Laude}
\end{list2}

\end{list1}

\begin{adjustwidth*}{-3.3cm}{-2cm}

\textbf{Publications}\\
\noindent\rule{8cm}{0.4pt}

\end{adjustwidth*}

\section{\sc Manuscripts under Revision}

Liu, S., Ullman, T.D., Tenenbaum J.B., and Spelke, E., The economist in the crib: Infants infer the value of goals from the costs of actions. \\(pending final acceptance in \textit{Science}).

Ullman, T.D. and McCoy, J.P., A minimal Turing test.\\ (pending final acceptance in \textit{J. Exp. Soc. Psychol.}).

Ullman, T.D. and McCoy, J.P., The plausible impossible: Judgments of effort for magical violations of intuitive physics.

Gerstenberg, T., Ullman, T., Nagel, J., Kleiman-Weiner, M., Lagnado, D., and Tenenbaum, J.B., Lucky or clever? From changed expectations to attributions of responsibility.

Kryven, M., Ullman, T. D., Cowan, W., and Tenenbaum, J. B., Strategy and Luck: Intuitive Theories of Attributed Intelligence.

\section{\sc Submitted Manuscripts}

Ullman, T.D. and Zimmerman, S., Models of transformative decision making (submitted to Transformative Experience, eds. Enoch Lambert and John Schwenkler, Oxford University Press).

Ullman, T.D., Kosoy, E., Tenenbaum J.B., and Spelke, E., Preschoolers' understanding of weight as an underlying dynamic variable in physical scenes (submitted to \textit{Child Development}).

\section{\sc Manuscripts in Prep}
%% move up 
Ullman, T.D., Xu, Y., and Goodman, N.D., The pragmatics of spatial language. 

Ullman, T.D., Baker, C.L., Macindoe, O., Evans, O., Goodman, N.D., and Tenenbaum, J.B. Helping and Hindering: Inferring higher-order social goals. 

\section{\sc Journal articles}

Ullman, T. D., Spelke, E. S., Battaglia, P., and Tenenbaum, J. B. (2017), Mind Games: Game Engines as an Architecture for Intuitive Physics. \textit{Trends in Cognitive Science, 21}(9), 649--665.

Ullman, T. D., Stuhlm{\"u}ller, A., Goodman, N.D., and Tenenbaum, J. B. (In press), Learning physical parameters from dynamic scenes. \textit{Cognitive Psychology.}

Lake, B. M., Ullman, T. D., Tenenbaum, J. B., and Gershman, S. J. (2017), Building machines that learn and think like people. \textit{Behavioral and Brain Sciences} 1--101.

Hamlin, J. K., Ullman, T. D., Tenenbaum, J. B., Goodman, N. D., and Baker, C. L. (2013), The mentalistic basis of core social cognition: Experiments in preverbal infants and a computational model. \textit{Developmental Science 16}(2), 209-226.

Ullman, T. D., Goodman, N. D., and Tenenbaum, J. B. (2012), Theory learning as stochastic search in the language of thought. \textit{Cognitive Development 27}(4), 455--480.

Goodman, N. D., Ullman, T. D., and Tenenbaum, J. B. (2012), Learning a theory of causality. \textit{Psychological Review, 118}(1), 110. 

\section{\sc Book Chapters}

Ullman, T.D., McCoy, J.P., and Paul, L.A., (forthcoming 2018). Modal Prospection. Metaphysics and Cognitive Science, eds. Alvin Goldman and Brian McLaughlin. Oxford University Press (US).

\section{\sc Peer Reviewed Conference Proceedings}

Ullman, T. D., Alonso-Diaz, S., Ferringo, S., Zahid, S., and Kidd, C. (2017), Weight matters: The role of physical weight in non-physical language across age and culture. \textit{Proceedings of the $39^{th}$ Annual Conference of the Cognitive Science Society.}

Liu, S., Ullman, T. D., Tenenbaum, J. B., and Spelke, E. S. (2017). What's worth the effort: Ten-month-old infants infer the value of goals from the costs of actions. \textit{Proceedings of the $39^{th}$ Annual Conference of the Cognitive Science Society.}

Kryven, M., Ullman, T. D., Cowan, W., and Tenenbaum, J. B. (2017). Thinking and guessing: Bayesian and empirical models of how humans search. \textit{Proceedings of the $39^{th}$ Annual Conference of the Cognitive Science Society.}

Chang, M. B., Ullman, T. D., Torralba, A., and Tenenbaum, J. B. (2017), A compositional object-based approach to learning physical dynamics. \textit{International Conference on Learning Representations (ICLR).}

Ullman, T.D., Xu, Y. \& Goodman, N.D. (2016). The Pragmatics of spatial language. \textit{Proceedings of the $38^{th}$ Annual Conference of the Cognitive Science Society.}

Ullman, T.D., Siegel, M., Tenenbaum, J.B. \& Gershman, S.J. (2016). Coalescing the vapors of human experience into a viable and meaningful comprehension. \textit{Proceedings of the $38^{th}$ Annual Conference of the Cognitive Science Society.}

Kryven, M., Ullman, T.D., Cowan, W. \& Tenenbaum, J.B. (2016). Outcome or strategy? A Bayesian model of intelligence attribution. \textit{Proceedings of the $38^{th}$ Annual Conference of the Cognitive Science Society.}

Gerstenberg, T., Ullman, T. D., Kleiman-Weiner, M., Lagnado, D. A. \& Tenenbaum, J. B. (2014). Wins above Replacement: Responsibility attributions as counterfactual replacements. \textit{Proceedings of the $36^{th}$ Annual Conference of the Cognitive Science society.}

Ullman, T.D., Stuhlm{\"u}ller A., Goodman, N.D. \& Tenenbaum, J.B. (2014). Learning physics from dynamical scenes. \textit{Proceedings of the $36^{th}$ Annual Conference of the Cognitive Science society.}

Bonawitz E., Ullman, T.D., Gopnik, A. \& Tenenbaum, J.B. (2012). Sticking to the evidence? A Computational and behavioral case Study of micro-theory change in the domain of magnetism, \textit{International Conference Developmental Learning and Epigenetic Robotics; best paper award: experiment combined with computational model.}

Ullman, T.D.*, McCoy, J.P.*, Stuhlmuller, A., Gerstenberg, T. \& Tenenbaum J.B. (2012). Why blame Bob? Probabilistic generative models, counterfactual reasoning, and blame attribution. \textit{Proceedings of the $33rd$ Annual Conference of the Cognitive Science Society.}

Ullman, T.D., Goodman, N.D. \& J. B. Tenenbaum (2010). Theory acquisition as stochastic search. \textit{Proceedings of the $32nd$ Annual Conference of the Cognitive Science Society.}

Ullman, T.D., Baker, C.L., Macindoe, O., Evans, O., Goodman, N.D. \& Tenenbaum, J.B. (2010). Help or hinder: Bayesian models of social goal inference. \textit{Advances in Neural Information Processing Systems (Vol. 22, pp. 1874-1882).}

Goodman, N.D., Ullman, T.D. \& Tenenbaum, J.B. (2009). Learning a theory of causality \textit{Proceedings of the $31st$ Annual Conference of the Cognitive Science Society.}

\vspace{20pt}
\begin{adjustwidth*}{-3.3cm}{-2cm}

\hspace{-3.8em}\textbf{Talks and Presentations}\\
\hspace*{-3.8em}\noindent\rule{8cm}{0.4pt}

\end{adjustwidth*}

\section{\sc }

Canonical Mass: Preschoolers Expectations of Dynamic Variables for Solid Objects,\\
Society for Research in Child Development, Austin, TX. 2017.

Modal Imagination,\\ Ranch Metaphysics Workshop, Tucscon, AZ. 2017.

People and Things,\\ Current Work in Developmental Psychology Colloquium. Boston College, MA. 2016. 

Development, Psychology, Physics. \\DeepMind Technologies, London. 2016. 

Modal Prospection \\ Philosophy Seminar. Rutgers University, NJ. 2016.

Imagining and Evaluating Possible Future Selves, \\ $42nd$ Meeting of the Society for Philosophy and Psychology. Austin, TX. 2016.

Computational Cognitive Science,\\ Interdisciplinary College on AI, Germany. 2016. 

Probabilistic Programming,\\ Interdisciplinary College on AI, Germany. 2016. 

Effort as a Bridge Across Action and Action Understanding,\\
The $20^{th}$ International Congress on Infant Studies. New Orleans, LA. 2016.

Children's Learning as Stochastic Search, \\Society for Research in Child Development. Philadelphia, PA. 2015.

Theories, Imagination, and the Generation of New Ideas, \\Center for Brains, Minds and Machines Summer School. Woods Hole, MA. 2015.

Probabilistic Programming Tutorial, \\ Center for Brains, Minds and Machines Summer School. Woods Hole, MA. 2015.

Theories of Physics, \\More on Development. Columbus, OH. 2015.

Modeling a Theory of the Self, \\Workshop on Transformative Experiences. Chicago, IL. 2015.

Deep Thoughts: The Value of Understanding,\\ Commentator at $41^{th}$ Meeting of the Society for Philosophy and Psychology. Duke University, NC. 2015.

Wins Above Replacement: Responsibility Attributions as Counterfactual Replacement,\\ $40^{th}$ Meeting of the Society for Philosophy and Psychology. Vancouver, Canada. 2014.

Theories, Imagination, and the Generation of New Ideas, \\Center for Brains, Minds and Machines Summer School. Woods Hole, MA 2014.

Probabilistic Programming Tutorial, \\ Center for Brains, Minds and Machines Summer School. Woods Hole, MA. 2014.

Learning Physics from Dynamic Scenes, \\$36^{th}$ Annual Meeting of the Cognitive Science Society. Quebec, Canada. 2014.

Theories, Imagination, and the Generation of New ideas,\\ Pre-conference debate at Child Development Society Meeting. Memphis, TN. 2013.

Help or Hinder? Bayesian Models of Social Goal Inference,\\ Simons Center, MIT. 2010.

Why Blame Bob? Probabilistic Generative Models and Blame Attribution,\\ $34^{th}$ Annual Meeting of the Cognitive Science Society. Sapporo, Japan. 2012.

Theory Learning as Stochastic Search,\\ $32nd$ Annual Meeting of the Cognitive Science Society. Portland, OR. 2010.

Help or Hinder? Bayesian Models of Social Goal Inference,\\ Machine Learning Summer School, Cambridge, UK. 2009.

Help or Hinder? Bayesian Models of Social Goal Inference,\\ $23rd$ Annual Conference on Neural Information Processing Systems. Vancouver. 2009.

\begin{adjustwidth*}{-17.8cm}{-2cm}

\hspace{-3.8em}\textbf{Other}\\
\hspace*{-3.8em}\noindent\rule{8cm}{0.4pt}

\end{adjustwidth*}

\section{\sc Teaching Experience and Outreach}

\begin{tabular}{@{}p{0.4in}p{0.3in}p{4in}}
2017 & & Lecturer and Teaching Assistant, CBMM summer school\\
2015 & & Lecturer and Teaching Assistant, CBMM summer school\\
2014 & & Lecturer and Teaching Assistant, CBMM summer school\\
2012 & & Teaching Assistant, Topics in early childhood cognition (MIT 9.85)\\
2011 & & Teaching Assistant, Cognitive processes (MIT 9.65)\\
2010 & & Planning committee member, Cambridge Science Festival\\
2009 & & Presenter and volunteer at Neuroscience Day, Museum of Science
\end{tabular}


\section{\sc Honors and Awards}

\begin{tabular}{@{}p{0.8in}p{4in}}
2011 & MIT Continued Dedication to Teaching award  \\
2010 & MIT Excellence in Teaching award  \\
2010 & National Science Foundation (NSF) fellowship\\
2009 & Singleton Graduate Fellowship \\
2009 & National Science Foundation (NSF) honorable mention\\
2004-2007 & Hebrew University of Jerusalem Scholarships of Excellence
\end{tabular}


\section{\sc Service}

Reviewer for: Cognition, Cognitive Psychology, Cognitive Development, Cognitive Science, Developmental Psychology, Proceedings of the Royal Society B, Philosophical Psychology, Neural Information Processing Systems (NIPS), The Annual Conference of the Cognitive Science Society

PC Member AAAI main track

Organizer of ``More on Development (MOD)'' (Ohio, 2015)

Co-Organizer of Child Development Society pre-conference on ``computational cognitive models and cognitive development'' (2014)

\section{\sc Students Mentored}

Felix Sosa (2017)

Cameron Nieters (2017)

Michael Chang (2016, 2017)

Eliza Kosoy (2016, 2017)

Heather Tarr (2016)

Alexandra Wheeler (2016)

Samuel Zimmerman (2016)

Marta Kryven (2016)


\section{\sc Membership}

Cognitive Science Society (CSS)

Society for Research in Child Development (SRCD)

Cognitive Development Society (CDS)

Society for Philosophy and Psychology (SPP)

Society for Personality and Social Psychology (SPSP)

\section{\sc Skills}

\begin{tabular}{@{}p{0.8in}p{6in}}

Languages:& English, Hebrew, some Latin\\
\\
Programming and tools:& Python, Church, Webppl, Javascript, Julia, Blender, Jupyter, and R \\

\end{tabular}


\section{\sc References}

{\bf Josh Tenenbaum}, Professor,
Brain and Cognitive Science, MIT,
 \texttt{jbt@mit.edu}

{\bf Laura Schulz}, Professor,
Brain and Cognitive Science, MIT,
 \texttt{lschulz@mit.edu}

{\bf Elizabeth Spelke}, Professor,
Psychology, Harvard,
\texttt{spelke@wjh.harvard.edu}

{\bf Noah Goodman}, Professor,
Psychology, Stanford University,
 \texttt{ngoodman@stanford.edu}\\

\end{resume}
\end{document}
